---
author: "Mark Christopher Adkins"
date: '`r paste("Created: 2020-09-12"," Last Modified: ", format(Sys.Date()))`'
title: 'Power'
output:
  html_document:
    toc_float: true
    toc_depth: 4
    number_sections: FALSE
    toc: true
    self_contained: true
    css: "../misc/style.css"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("HTML Exercises"))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pwr)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```

## Power

To conduct a power analysis, we will use a function from the {pwr} package. We specify the sample size (*n*), the significance level (*sig.level*), and the effect size (*d*) we want to be able to detect.

```{r}
# conduct the the power of the test to detect an effect size of d = .2
pwr.t.test(n = 16,
           sig.level = .05,
           d = .2)
```
```{r echo=FALSE}
# conduct the the power of the test to detect an effect size of d = .2
power_results <- pwr.t.test(n = 16,
           sig.level = .05,
           d = .2)
```

If this study were repeated numerous times using the same sample size, and sampling from the same population, about `r round(power_results$power,3)*100` percent of those studies would detect a effect at least as large as `r power_results$d`.

## Power

To conduct a power analysis, we will use a function from the {pwr} package. We specify the sample size (*n*), the significance level (*sig.level*), and the effect size (*d*) we want to be able to detect. We also need to tell the function that we want the power for a paired t-test.

```{r}
pwr.t.test(n = 5,
           d = .2,
           sig.level = .05,
           type = "paired")
```

